\textsf{Are frontier models superhuman chemists?}

### 2024-03-19 src/tex/ms.tex
try to fix the requires-calculation subset

\clearpage
\begin{refsection}
\section{Introduction}
\Glspl{llm} are \gls{ml} models trained on massive amounts of text to complete sentences. 
Aggressive scaling of the models has led to a rapid increase in their capabilities,\autocite{brown2020language} with the leading models now being able to pass the BAR exam or identify and autonomously buy chemicals when augmented with external tools such as web search and synthesis planners.\autocite{openai2024gpt4}
While some see in them \enquote{sparks of \gls{agi}},\autocite{bubeck2023sparks} others consider them as \enquote{stochasitc parrots}---i.e., systems that only regurgitate what they have been trained on.\autocite{bender2021dangers}
In any case, the promise of so-called foundation models (the leading ones being called frontier models) is that they show the ability solve a wide variety of tasks they have not been explicitly trained on.\autocite{bommasani2021opportunities, anderljung2023frontier}
This led to tremendous economic interest and investment in those generative models, with an expected market of more than \$1.3 trillion (almost \$30 billion for drug discovery applications) by 2032.\autocite{bloomberg}

>>>>

\clearpage
\begin{refsection}
\section{Introduction}
\Glspl{llm} are \gls{ml} models trained on massive amounts of text to complete sentences. 
Aggressive scaling of the models has led to a rapid increase in their capabilities,\autocite{brown2020language,zhong2024benchmarking} with the leading models now being able to pass the BAR exam or identify and autonomously buy chemicals when augmented with external tools such as web search and synthesis planners.\autocite{openai2024gpt4}
While some see in them \enquote{sparks of \gls{agi}},\autocite{bubeck2023sparks} others consider them as \enquote{stochasitc parrots}---i.e., systems that only regurgitate what they have been trained on.\autocite{bender2021dangers}
In any case, the promise of so-called foundation models (the leading ones being called frontier models) is that they show the ability solve a wide variety of tasks they have not been explicitly trained on.\autocite{bommasani2021opportunities, anderljung2023frontier}
This led to tremendous economic interest and investment in those generative models, with an expected market of more than \$1.3 trillion (almost \$30 billion for drug discovery applications) by 2032.\autocite{bloomberg}
